|

### 2022-03-27 07-Chp-Triangulation.Rmd
Fixed equation and LDL-c/HDL-c

\blandscape
<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) __Summary of research designs included in this thesis__ -The research projects performed as part of this thesis and used as evidence sources in this triangulation exercise are summarised. Note that Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.

@@

```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
\elandscape

@@

Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the individual participant data (IPD) analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (in the systematic review: TC - `r obsLipids$Dementia_TC$estimate`; LDL - `r obsLipids$Dementia_LDL$estimate`; HDL - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate` ). Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`). Finally, a meta-analysis of RCTs of statin use (`r rct_statin_acd`) and of MR analyses of genetic instruments that mimic statin use (`r mrStatin$Dementia$estimate`) found weak evidence of an association, providing indirect evidence on the effect of lipid lowering on this outcome.

@@

Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (in the systematic review: TC - `r obsLipids$AD_TC$estimate`; LDL - `r obsLipids$AD_LDL$estimate`; HDL - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`). Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`). A meta-analysis of MR analyses of genetic instruments that mimic statin use found weak evidence for an association of lipid lowering with Alzheimer's disease (`r mrStatin$AD$estimate`).

@@

Under the  method reported in Turner _et al._,[@turner2009], total additive bias (denoted using subscript $\delta$) in result $i$ is then described by mean $\mu_{i\delta}$ and variance $\sigma_{i\delta}^{2}$, which are simply the sum of the mean and variance of all additive biases in the $i$th result. Similarly, the total proportional bias (denoted using subscript $\beta$) in the $i$th result is described by mean $\mu_{i\beta}$ and variance ${\sigma_{i\beta}}^2$. This are defined as

\begin{equation}
  \mu_{i\beta} = exp(\alpha_{i} + {\psi_i}^2)
  (\#eq:prop-total-mean)
\end{equation}

@@

where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness, respectively. Note that in this exercise, the total additive indirectness $\mu_{i\beta}^{\mathrm{In}} = 1$ because all indirectness was defined _a priori_ as being proportional.

>>>>

\blandscape

<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) __Summary of research designs included in this thesis__ -The research projects performed as part of this thesis and used as evidence sources in this triangulation exercise are summarised. Note that Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.

@@

```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

\elandscape

@@

Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the individual participant data (IPD) analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (in the systematic review: TC - `r obsLipids$Dementia_TC$estimate`; [LDL-c]{.correction} - `r obsLipids$Dementia_LDL$estimate`; [HDL-c]{.correction}
 - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate` ). Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`). Finally, a meta-analysis of RCTs of statin use (`r rct_statin_acd`) and of MR analyses of genetic instruments that mimic statin use (`r mrStatin$Dementia$estimate`) found weak evidence of an association, providing indirect evidence on the effect of lipid lowering on this outcome.

@@

Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (in the systematic review: TC - `r obsLipids$AD_TC$estimate`; [LDL-c]{.correction} - `r obsLipids$AD_LDL$estimate`; [HDL-c]{.correction} - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`). Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`). A meta-analysis of MR analyses of genetic instruments that mimic statin use found weak evidence for an association of lipid lowering with Alzheimer's disease (`r mrStatin$AD$estimate`).

@@

Under the  method reported in Turner _et al._,[@turner2009], total additive bias (denoted using subscript $\delta$) in result $i$ is then described by mean $\mu_{i\delta}$ and variance $\sigma_{i\delta}^{2}$, which are simply the sum of the mean and variance of all additive biases in the $i$th result. Similarly, the total proportional bias (denoted using subscript $\beta$) in the $i$th result is described by mean $\mu_{i\beta}$ and variance ${\sigma_{i\beta}}^2$. This are defined as
```{block type='correction'}
\begin{equation}
  \mu_{i\beta} = exp(\alpha_{i} + {\psi_i}^2/2)
  (\#eq:prop-total-mean)
\end{equation}
```

@@

where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness, respectively. Note that in this exercise, the total additive indirectness $\mu_{i\delta}^{\mathrm{In}} = 1$ because all indirectness was defined _a priori_ as being proportional.
